Defining Crete's Macroecology based on its soil Microbial Interactome

### 2023-12-23 manuscript.tex
add ref

Crete has been studied since the classical times for its' fauna \citep{Sidiropoulos_Polymeni_Legakis_2017}, flora \citep{Krimbas_2005} and environment in general.

@@

\bibliographystyle{plain}
\bibliography{reference}

>>>>

The island of Crete, Greece has been studied since the classical times for its' fauna \citep{Sidiropoulos_Polymeni_Legakis_2017}, flora \citep{Krimbas_2005} and ecosystems \citep{Grove1993}.

@@

\bibliographystyle{unsrt}
\bibliography{reference}
